Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-23 manuscript/draft.Rmd
fix gbm ref
remove duplicate, and "other" authors which was causing issues.

**"Macroecological" model: richness GBM.** We used a boosted regression tree
model using the `gbm` package [@ridgeway2017] to directly model species richness
as a function of environmental variables. Boosted regression trees are a form of
tree-based modeling that work by fitting thousands of small tree-structured
models sequentially, with each tree optimized to reduce the error of its
predecessors. They are flexible models that are considered well suited for
prediction [@elith2008]. This model was optimized using a Gaussian likelihood,
with a maximum interaction depth of 5, shrinkage of 0.015, and up to 10,000
trees. The number of trees used for prediction was selected using the "out of
bag" estimator; this number averaged `r numbers$n_gbm[1]` for the non-observer
data and `r numbers$n_gbm[2]` for the observer-corrected data.

>>>>

**"Macroecological" model: richness GBM.** We used a boosted regression tree
model using the `gbm` package [@gbm] to directly model species richness
as a function of environmental variables. Boosted regression trees are a form of
tree-based modeling that work by fitting thousands of small tree-structured
models sequentially, with each tree optimized to reduce the error of its
predecessors. They are flexible models that are considered well suited for
prediction [@elith2008]. This model was optimized using a Gaussian likelihood,
with a maximum interaction depth of 5, shrinkage of 0.015, and up to 10,000
trees. The number of trees used for prediction was selected using the "out of
bag" estimator; this number averaged `r numbers$n_gbm[1]` for the non-observer
data and `r numbers$n_gbm[2]` for the observer-corrected data.
